\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Personal Interests in Economics and Data Science}
\author{Daniel Carpenter}
\date{January 2020}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Summary Paragraph}

Practical applications of modeling and optimization primarily drive my personal interests for data science and economics. One year ago, I had taken my first econometrics course, which I was able to learn more about causal inference while equipping myself with R as a tool to practically apply the discussed methods. Alongside my growing interest while in this class, I interned for (and currently do) an internal consulting group within the Chickasaw Nation Department of Commerce. This department included data scientists and other business-related individuals. The pairing of these two groups allowed me to better understand the applications of data science on operations management and consultation. I saw the optimization projects that these data scientists worked on, and I at once found interest in this field. My finance background consisted primarily of excel modeling, which I felt inferior after seeing these applications of data science. I plan to finish my two undergraduate majors in finance and economics, then pursue a master’s in data science while working for this consulting group.

I plan to discuss ideas for my project with individuals that I work with, so that I am able to apply the materials that I learn in this class towards my future career. Currently, I do not have a clear idea of what that project may be, but I can obtain transactional data from any of the business operations that the Nation has. Additionally, there is a potential area of opportunity for contingency planning amidst the Oklahoma government’s debate of the Model Gaming Compact. 

\section{Equation}
\begin{equation}
    a^2 + b^2 = c^2
\end{equation}

\end{document}